DDSAnalytics  - Employee Trends

### 2018-04-16 msds6371-group-project-kaggle.Rmd
Spell check

This dataset, is roughly 441k with 1459 observation of 80 variables.  This has one less observation: SalesPrices.  This is due to the fact it is meant to be used for cross-validation, and does not require this variable because we are meant to predict that with our models.

@@

We need to perform outlier analysis and peform transformations to address equal deviation and normality.

@@

For brevity, some of the interative process for analyzing the data is omitted, but summarised here.  It was found that there was no statistical difference between the BrkSide and Edwards neighborhoods, so these were combined into a single entity.  Also, to address the high VIF values, the interaction variables were centered.

### Assumptions
When looking at the Log-Log transformed data in Image 004, the linear relationship looks much better.  Also,, when looking at the fit diagnostics in Image 005, we can se that the assumptions are addressed:
1.There is a clear linear trend with explanatory variables with the LogSalePrice
1. The histogram looks better and the QQ plot as well, combined with the large number of observations, we can say the data ius normal
1. All residual plots look like a good random cloud with equal variace across the graph
1. For independence, we do not know how the data were collected, and will assume that they are independent

@@

After analyzing the scatterplots, we noticed the two observations that were from homes over 4500 square feet.  Since these two observations have high leverage, we decided to try to find other effects these observations might have. Looking at the group ranking of these observations we decided to remove these observations due to the effect these had on our model assumptions.  We were more interested in the observations that were centered around the middle of the ranking.

@@

| Models        | Adusted R^2 | CV Press    |
|---------------|-------------|-------------|
| Untransformed | 0.5696      | 4.00198 E12 |
| Log-Log       | 0.5808      | 97.939      |

Image 007 and Image 008 capture the SAS output for the Untransformned and Log-Log transformed models respectively.

>>>>

This dataset, is roughly 441k with 1459 observation of 80 variables.  This has one less observation: SalePrice.  This is due to the fact it is meant to be used for cross-validation, and does not require this variable because we are meant to predict that with our models.

@@

We need to perform outlier analysis and perform transformations to address equal deviation and normality.

@@

For brevity, some of the iterative process for analyzing the data is omitted, but summarized here.  It was found that there was no statistical difference between the BrkSide and Edwards neighborhoods, so these were combined into a single entity.  Also, to address the high VIF values, the interaction variables were centered.

### Assumptions
When looking at the Log-Log transformed data in Image 004, the linear relationship looks much better.  Also,, when looking at the fit diagnostics in Image 005, we can see that the assumptions are addressed:
1.There is a clear linear trend with explanatory variables with the LogSalePrice
1. The histogram looks better and the QQ plot as well, combined with the large number of observations, we can say the data is normal
1. All residual plots look like a good random cloud with equal variance across the graph
1. For independence, we do not know how the data were collected, and will assume that they are independent

@@

After analyzing the scatter plots, we noticed the two observations that were from homes over 4500 square feet.  Since these two observations have high leverage, we decided to try to find other effects these observations might have. Looking at the group ranking of these observations we decided to remove these observations due to the effect these had on our model assumptions.  We were more interested in the observations that were centered around the middle of the ranking.

@@

| Models        | Adjusted R^2 | CV Press    |
|---------------|--------------|-------------|
| Untransformed | 0.5696       | 4.00198 E12 |
| Log-Log       | 0.5808       | 97.939      |

Image 007 and Image 008 capture the SAS output for the Untransformed and Log-Log transformed models respectively.
